Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations

### 2013-07-28 Doc/Vrst2013/vrst2013.tex
using acmsiggraph class
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@600 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

% TODO
% REMEMBER: After having produced the .bbl file, and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.

\documentclass{acm_proc_article-sp}

\usepackage{caption}
\DeclareCaptionType{copyrightbox}
\usepackage{amsmath}
%\usepackage{makeidx}
%\usepackage[pdftex]{graphicx} ... we have to use ps/eps
\usepackage{subfig}

@@

%%% Comments
\usepackage{color}
\newcommand{\TG}[1]{{\color{blue}\textbf{TG: #1}}}
\newcommand{\CD}[1]{{\color{green}\textbf{CD: #1}}}
\newcommand{\IP}[1]{{\color{cyan}\textbf{IP: #1}}}
\newcommand{\TODO}[1]{{\color{red}\textbf{TODO: #1}}}
%%%

@@

@@

\title{Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations}
%\subtitle{}

\numberofauthors{4}
\author{
% 1st. author
\alignauthor
Tom\'a\v{s} Golembiovsk\'y\\
       \affaddr{Faculty of Informatics}\\
       \affaddr{Masaryk University}\\
       \affaddr{Brno, Czech Republic}\\
       \email{nyoxi@ics.muni.cz}
% 2nd. author
\alignauthor
Igor Peterl\'ik\\
       \affaddr{Institut Hospitalo-Universitaire}\\
       \affaddr{Strasbourg, France}\\
       \email{Igor.Peterlik@ihu-strasbourg.eu}
% 3rd. author
\alignauthor
Christian Duriez\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{Christian.Duriez@inria.fr}
\and
% 4th. author
\alignauthor
St\'ephane Cotin\\
       \affaddr{INRIA}\\
       \affaddr{Lille, France}\\
       \email{Stephane.Cotin@inria.fr}
}

%\date{30 May 2013}

@@

% Categories
\category{I.6.5}{Simulation and Modeling}{Model Development}
\category{J.3}{Life and Medical Sciences}{Health}

\terms{Modeling and Simulation}

% NOT required for Proceedings
\keywords{deformable liver model, Glisson's capsule, real-time soft tissue modeling}

@@

\bibliographystyle{abbrv}
\bibliography{bibdata}

>>>>

\documentclass[sposored]{acmsiggraph}

\usepackage{amsmath}
\usepackage{subfig}

@@

@@

\title{Modeling Liver with Glisson's Capsule in Real-Time Medical Simulations}

%TODO
\author{
\begin{tabular}[t]{cccc}%
  Tom\'a\v{s} Golembiovsk\'y\thanks{nyoxi@ics.muni.cz} &
  Igor Peterl\'ik &
  Christian Duriez &
  St\'ephane Cotin \\
%
  Faculty of Informatics &
  Institut Hospitalo-Universitaire &
  INRIA &
  INRIA \\
%
  Masaryk University &
  Strasbourg, France &
  Lille, France &
  Lille, France \\
%
  Brno, Czech Republic
\end{tabular}
}
%\affiliation{foobar}
%\numberofauthors{4}
%\author{%
%Tom\'a\v{s} Golembiovsk\'y\\
%       \affaddr{Faculty of Informatics}\\
%       \affaddr{Masaryk University}\\
%       \affaddr{Brno, Czech Republic}\\
%       \email{nyoxi@ics.muni.cz}
%% 2nd. author
%\alignauthor
%Igor Peterl\'ik\\
%       \affaddr{Institut Hospitalo-Universitaire}\\
%       \affaddr{Strasbourg, France}\\
%       \email{Igor.Peterlik@ihu-strasbourg.eu}
%% 3rd. author
%\alignauthor
%Christian Duriez\\
%       \affaddr{INRIA}\\
%       \affaddr{Lille, France}\\
%       \email{Christian.Duriez@inria.fr}
%\and
%% 4th. author
%\alignauthor
%St\'ephane Cotin\\
%       \affaddr{INRIA}\\
%       \affaddr{Lille, France}\\
%       \email{Stephane.Cotin@inria.fr}
%}
\pdfauthor{Tom\'a\v{s} Golembiovsk\'y}

@@

@@

% Categories
\begin{CRcatlist}
  \CRcat{I.6.5}{Simulation and Modeling}{Model Development}
  \CRcat{J.3}{Life and Medical Sciences}{Health};
\end{CRcatlist}

\keywords{deformable liver model, Glisson's capsule}

\keywordlist

\TOGlinkslist

\copyrightspace

@@

\bibliographystyle{acmsiggraph}
\bibliography{bibdata}
